%!TEX root = ../Project.tex
\section{Context Survey} 
\label{Context_Survey}

\subsection{Evolution of Tactical RPGs } % (fold)
\label{sub:evolution_of_tactical_rpgs_}

Notable TRPGs
\begin{itemize}
	\item Bokosuka Wars  - probably the first TRPG
	\item Fire Emblem: Ankoku Ryu to Hikari no Tsurugi  -  First popular TRPG.  Characters are unique
	\item Tactical Ogre:  
	\begin{itemize}
		\item  First TRPG with isometric graphics.
		\item Character battle order is determined by the character's `speed' rather, each player moves all their units when its their turn.
		\item  First to have a branching plot and the player's choice effecting the game.
		\item  Associated the genre with the word `Tactics', used by many later games
	\end{itemize}      
	\item Final Fantasy Tactics, widely popular, based on Tactics Ogre.
	\item Disgaea: Hour of Darkness:  Allows the player to play random generated maps. The latest in the series is one of the few TRPGs that contain a map editor.  
	\item Recent game, have mostly mix aspects from other genres, for example Valkyria Chronicles features FPS like shoting when attacking.
\end{itemize}

% subsection evolution_of_tactical_rpgs_ (end)

\subsection{Overview of Game Engines} % (fold)
\label{sub:overview_of_game_engines}

\begin{itemize}
	\item \texttt{Sim RPG Maker 95}, one of the few tactical RPG's engines
	\item \texttt{RPG Maker} which it is based off. 
	\item Mention  engines such \texttt{unity} or \texttt{unreal}  which used to make TRPGs?  
\end{itemize}

% subsection overview_of_game_engines (end)