%CS4099 Dissetation
%!TEX root = ../Project.tex
\section{Objectives}

\begin{figure}[h!]
	\caption*{Key}
	\begin{center}
		\begin{tabular}{rl}
		\Checkmark & Finished\\
		\XSolidBrush & Not Started\\
		– $\bullet$ $\star$ & In progress\\
		\end{tabular}
	\end{center}
\end{figure}

\label{Objectives}
\subsection{Primary}
\label{primary}
The main goal of the primary objectives is allow the user to create a complex Tactical RPG, with limited customisability.  
\begin{itemize}
\item To develop an engine that takes:
\begin{itemize}

 \item The definition of character attributes and a combat system.
	\item The definition of a world broken up into the smaller environments.
	\begin{itemize}
		\item The rules of the game.
		\cross The kinds of enemies.
	\end{itemize}
	
	\tick The definition of simple story as a wrapper for the whole game, from the start to the conclusion of the game
	\begin{itemize}
		\cross Which is told between the movement between different environments.
	\end{itemize}
	                        
	\cross The set of selected character attributes.
	
\end{itemize}
and create a playable tactic RPG.

\item To include in the engine support for the following:
\begin{itemize}
	\tick \texttt{units} with a fixed set of associated attributes such as:
	\begin{itemize}
		\tick Hit-points (which represent the health of the unit).
		\tick Strength.
		\tick Defence.
		\tick Move (The number of tiles the unit can move each turn).
	\end{itemize}
	
	\item \texttt{battles} which take place on grid and include:
	\begin{itemize}
		\tick  A set number of \texttt{units} for each player.
		\item  A Winning \texttt{condition} such as defeat all of the other players units.
		\tick  Battles are \texttt{turn based} meaning that each player moves all their units (once) before the next player turn.   
		\item  A combat system.
	\end{itemize}
	
	\item A combat system that includes
		\begin{itemize}
			\tick \texttt{combat} between adjacent units.
			\begin{itemize}
				\tick When the unit hit-points are reduced to zero they are \texttt{defeated} and are removed from the map
			\item A set of rules that govern the combat.
			\end{itemize}
			
		\end{itemize}
	
	\item A predefined set of behaviours for how the non-player characters should behave.
	\begin{itemize}
		\tick Including pathfinding.
	\end{itemize}
	
	\tick A isometric graphical representation of the game.
	\begin{itemize}
		\tick Which is show the grid with all the units.
		\tick Allow the user to move their units and see the opponents moves.
		\tick Allows the user to attack the opponents units.
		\tick Which allows the user to see a unit status (e.g current hit points).
		\tick Text will be to describe the more complex actions such magic.
	\end{itemize}
\end{itemize}
\end{itemize}

\subsection{Secondary}
\label{secondary}
The main goal of the secondary objectives is allow the user more customisability. 
\begin{itemize}
	\tick Tiles have \texttt{height}, where units can only move to tiles of a smilier height.
	\cross Tiles that are not passable such as sea, lava, etc.
	
	\tick Tiles have different movement costs associated with them.
	
	\item Players have items such as weapons that affect the result of combat between units. 
	\begin{itemize}
		\tick Including  Long distance weapons for the  player and AI.
	\end{itemize}
	
	\cross Direction and height of the character's tile affects attack.
	
	\tick Sound effects.
	\tick Music.
	
	\cross Saving and loading games.
	
	\item Allow the user to specify some of behaviour of non-player characters
	\begin{itemize}
		\cross Through the use of scripting.
		\cross An example: always attack a certain kind of unit or always attack the unit with the least Hit Points.
	\end{itemize}
	
	\item A graphical view to allow user specify the input to the engine.
\end{itemize}

\subsection{Tertiary} 
\label{tertiary}
The goal of the Tertiary objectives are provide the user with more customisability and to provide a GUI for simple scripts. 

\begin{itemize}
	\cross Custom events
	\begin{itemize}
		\item Attached to units or titles, could be used for:
		\begin{itemize}
			\item Making the player win if some enemies unit has less then 50\% Hit Points.
			
			\item Damaging a character if step on a specified.
			
			\item Showing some part of the story when a player's character reach a specified tile.
		\end{itemize}
	\end{itemize}
	
	\item A graphical editor for:
	\begin{itemize}
		\tick   making custom maps,
		\tick   making animations.
		\cross  specifying the input to the engine.
		\cross  making events
		\cross  Scripts for simple event such as `Defeat the leader' as a winning condition.
	\end{itemize}
	
	\tick Animations for units and movement.
\end{itemize}