% Abstract and Declaration
%!TEX root = ../Project.tex

%FIXME finish
\begin{abstract}

A Tactical RPG are games that are comprised of a series of battles, which take place in various environments intertwined with an over-arching story. Battle are similar to the game of chess but include RPG elements. These including attributes such as \emph{Hit Point} which represents how much damage a piece can receive before being defeated.  The aim of this project is  to develop an engine that affords the user a high degree of customisability. This is in addition to a isometric view of the battles and an editor which allows the user to visually specify the aspects of the engine. This reports discusses the process of creating the system, starting from the objectives of the project, following on with the design and implementation.  To conclude a critical evaluation of the project in regards of the objectives and related works will be detailed. The use of user testing and an example game's will be used to demonstrate the the project's capabilities.

\end{abstract}
\addcontentsline{toc}{section}{Abstract}

\sectionfont{
	\sectionrule{0pt}{0pt}{-10pt}{0.8pt}
}

\section*{Declaration}
\addcontentsline{toc}{section}{Declaration}
I declare that the material submitted for assessment is my own work except where credit is explicitly given to others by citation or acknowledgement. This work was performed during the current academic year except where otherwise stated.

%FIXME add word count
The main text of this project report is words NN,NNN* long, including project specification and plan. 

In submitting this project report to the University of St Andrews, I give permission for it to be made available for use in accordance with the regulations of the Declaration University Library. I also give permission for the title and abstract to be published and for copies of the report to be made and supplied at cost to any bona fide library or research worker, and to be made available on the World Wide Web. I retain the copyright in this work.